Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Community Detection and Parameter Estimation

### 2021-03-02 summary.Rmd
typo

Then Theorem 6 of \citet{pmlr-v28-wang13}, (\ref{eq:delta-conv}) and
(\ref{eq:thm5-proof}) imply that the SSC detection property holds as 
$n \to infty$ with probability 1.

>>>>

Then Theorem 6 of \citet{pmlr-v28-wang13}, (\ref{eq:delta-conv}) and
(\ref{eq:thm5-proof}) imply that the SSC detection property holds as 
$n \to \infty$ with probability 1.
